### 2016-04-22 msmfs.tex
Mostly complete to and including section 7

\usepackage[sans]{tcc_doc} % SDP style file
\usepackage[english]{babel}
\usepackage{amssymb,amsmath} % for the math symbols
\usepackage{mdwlist}
\usepackage{geometry}
\usepackage{marginnote}
\usepackage{datetime}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{mathtools}
\usepackage{hhtensor}
\graphicspath{ {images/} }

@@

% Add here the abbreviations used in your document
\sdplistofabbreviations
\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{6em}}
    \item[CDR] Critical Design Review \vspace{-0.2cm}
    \item[CPU] Central Processing Unit\vspace{-0.2cm}
    \item[CSP] Central Signal Processor\vspace{-0.2cm}
    \item[CUFFT] \textcolor{red}{Define it.}\vspace{-0.2cm}
    \item[DFT] \textcolor{red}{Only used once, in a title. Remove/expand?}\vspace{-0.2cm}
    \item[DM] \textcolor{red}{Define it.}\vspace{-0.2cm}
    \item[EoR] Epoch of Reionisation\vspace{-0.2cm}
    \item[FFT] Fast Fourier Transform\vspace{-0.2cm}
    \item[FLOP] Floating Point Operations \vspace{-0.2cm}
    \item[FLOPS] Floating Point Operations per Second \vspace{-0.2cm}
    \item[FoV] Field of View\vspace{-0.2cm}
    \item[GPU] Graphics Processing Unit \vspace{-0.2cm}
    \item[ICD] Interface Control Document\vspace{-0.2cm}
    \item[LMA] Levenberg-Marquardt Algorithm \vspace{-0.2cm}
    \item[LOFAR] LOw Frequency ARray\vspace{-0.2cm}
    \item[LSM] Local Sky Model\vspace{-0.2cm}
    \item[MS-MFS] Multi-Scale Multi-Frequency Synthesis\vspace{-0.2cm}
    \item[NVRAM] \textcolor{red}{Define it.} \vspace{-0.2cm}
    \item[OCLD] Optimised Candidate List and Data \vspace{-0.2cm}
    \item[PDR] Preliminary Design Review\vspace{-0.2cm}
    \item[RFI] Radio Frequency Interference\vspace{-0.2cm}
    \item[PSF] \textcolor{red}{Define it.} \vspace{-0.2cm}
    \item[PSS] Pulsar Search\vspace{-0.2cm}
    \item[PST] Pulsar Timing\vspace{-0.2cm}
    \item[SDP] Scientific Data Processor\vspace{-0.2cm}
    \item[SKA] Square Kilometre Array\vspace{-0.2cm}
    \item[SKAO] SKA Organisation\vspace{-0.2cm}
    \item[WCS] \textcolor{red}{Define it.} \vspace{-0.2cm}
%    \item[] \vspace{-0.2cm}
\end{basedescript}

@@

\newcommand{\dg}{^\dag}
\newcommand{\X}{\vec{x}}
\newcommand{\Xd}{\vec{{x}^\dag}}
\newcommand{\B}{\vec{b}}
\newcommand{\Bd}{\vec{b^\dag}}
\newcommand{\A}{{\tens{A}}}
\newcommand{\Ad}{{\tens{A^\dag}}}
\newcommand{\F}{{\tens{F}}}
\newcommand{\Fd}{{\tens{F^\dag}}}
\newcommand{\He}{{\tens{H}}}
\newcommand{\Sa}{{\tens{S}{N}}}
\newcommand{\Sd}{{\tens{S^\dag}}}
\newcommand{\Sna}{\tens{{S_{\nu}}{N}}}
\newcommand{\Snd}{\tens{{S_{\nu}^\dag}}}
\newcommand{\T}{{\tens{T}}}
\newcommand{\W}{{\tens{W}}}
\newcommand{\Wd}{{\tens{W^\dag}}}
\newcommand{\Pb}{{P_b}}

\newcommand{\Wim}{{\tens{W^{im}}}}
\newcommand{\Wimd}{{\tens{{W^{im}}^\dag}}}
\newcommand{\Wnt}{{\tens{W^{mfs}_t}}}
\newcommand{\Wntd}{{\tens{{W^{mfs}_t}^\dag}}}
\newcommand{\Wnp}{{\tens{W^{mfs}_p}}}
\newcommand{\Wnpd}{{\tens{{W^{mfs}_p}^\dag}}}
\newcommand{\Wnq}{{\tens{W^{mfs}_q}}}
\newcommand{\Wnqd}{{\tens{{W^{mfs}_q}^\dag}}}
\newcommand{\Wimn}{{\tens{W^{im}_{\nu}}}}
\newcommand{\Wimnd}{{\tens{{W^{im}_{\nu}}^\dag}}}

\newcommand{\wnt}{{w_{\nu}^t}}
\newcommand{\wnq}{{w_{\nu}^q}}
\newcommand{\wntq}{{w_{\nu}^{t+q}}}
\newcommand{\Wntn}{{\tens{w^{mfs}_{t,\nu}}}}
\newcommand{\Wntnd}{{\tens{{w^{mfs}_{t,\nu}}^\dag}}}
\newcommand{\Wnpn}{{\tens{W^{mfs}_{p,\nu}}}}
\newcommand{\Wnpnd}{{\tens{{W^{mfs}_{p,\nu}}^\dag}}}

@@

@@

\section{Scope of the document}

\section{Background}

@@

A canonical major/minor cycle algorithm is shown in Figure \ref{fig:major/minor}. The two functions Predict and MakeImage are sub-pipelines. ASKAPSoft and CASA both follow this form but with different ways of performing Predict (\ref{fig:predictuv} and \ref{fig:predictimage}) and MakeImage (\ref{fig:makeimageuv} and \ref{fig:makeimageimage})

@@

The MSMFS algorithm decomposes the image into a set of blobs, using a greedy algorithm in which the peak (in scale space) is found by searching for the peak in the reference frequency residual images each convolved with scale. For bright pixels, the principal solution is calculated by applying the inverse Hessian of the PSF convolved with scale. For faint pixels, just the peak in the reference frequency image is used.

@@

@@

@@

@@

\clearpage
\section{Serial and Parallel implementations}

\subsection{Serial}
\label{sec:serial}

The serial algorithm is as shown in Figure \ref{fig:algoCASA}.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\textwidth]{./algorithm.pdf}
  \caption{The MSMFS algorithm as implemented in CASA [RD??]}
  \label{fig:algoCASA}
\end{figure}

>>>>

\usepackage[sans]{tcc_doc} % SDP style file
\usepackage[english]{babel}
\usepackage{amssymb,amsmath} % for the math symbols
\usepackage{mdwlist}
\usepackage{geometry}
\usepackage{marginnote}
\usepackage{datetime}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{mathtools}
\usepackage{hhtensor}
\usepackage{color}
\usepackage{txfonts}

%\usepackage{stylefiles/fmtcount}
\usepackage{natbib}

\graphicspath{ {images/} }

@@

% Add here the abbreviations used in your document
\sdplistofabbreviations
\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{6em}}
    \item[CDR] Critical Design Review \vspace{-0.2cm}
    \item[FFT] Fast Fourier Transform\vspace{-0.2cm}
    \item[FLOP] Floating Point Operations \vspace{-0.2cm}
    \item[FLOPS] Floating Point Operations per Second \vspace{-0.2cm}
    \item[FoV] Field of View\vspace{-0.2cm}
    \item[MS-MFS] Multi-Scale Multi-Frequency Synthesis\vspace{-0.2cm}
    \item[PSF] Point Spread Function \vspace{-0.2cm}
    \item[SDP] Scientific Data Processor\vspace{-0.2cm}
    \item[SKA] Square Kilometre Array\vspace{-0.2cm}
    \item[SKAO] SKA Organisation\vspace{-0.2cm}
%    \item[] \vspace{-0.2cm}
\end{basedescript}

@@

\newcommand{\dg}{^\dag}
\newcommand{\X}{\vec{x}}
\newcommand{\Xd}{\vec{{x}^\dag}}
\newcommand{\B}{\vec{b}}
\newcommand{\Bd}{\vec{b^\dag}}
\newcommand{\V}{\vec{V}}
\newcommand{\Vd}{\vec{V^\dag}}
\newcommand{\A}{{\tens{A}{s}}}
\newcommand{\Ad}{{\tens{A^\dag}{s}}}
\newcommand{\F}{{\tens{F}{s}}}
\newcommand{\Fd}{{\tens{F^\dag}{s}}}
\newcommand{\He}{{\tens{H}{s}}}
\newcommand{\Sa}{{\tens{S}{s}}}
\newcommand{\Sd}{{\tens{S^\dag}{s}}}
\newcommand{\Sna}{\tens{{S_{\nu}}{s}}}
\newcommand{\Snd}{\tens{{S_{\nu}^\dag}{s}}}
\newcommand{\T}{{\tens{T}{s}}}
\newcommand{\W}{{\tens{W}{s}}}
\newcommand{\Wd}{{\tens{W^\dag}{s}}}
\newcommand{\Pb}{{\vec{P}}}

%\newcommand{\Wim}{{\tens{W^{im}}}}
%\newcommand{\Wimd}{{\tens{{W^{im}}^\dag}}}
%\newcommand{\Wnt}{{\tens{W^{\rm {mfs}}_t}}}
%\newcommand{\Wntd}{{\tens{{W^{\rm {mfs}}_t}^\dag}}}
%\newcommand{\Wnp}{{\tens{W^{\rm mfs}_p}}}
%\newcommand{\Wnpd}{{\tens{{W^{\rm mfs}_p}^\dag}}}
%\newcommand{\Wnq}{{\tens{W^{\rm mfs}_q}}}
%\newcommand{\Wnqd}{{\tens{{W^{\rm {mfs}}_q}^\dag}}}
%\newcommand{\Wimn}{{\tens{W^{im}_{\nu}}}}
%\newcommand{\Wimnd}{{\tens{{W^{im}_{\nu}}^\dag}}}

\newcommand{\Wim}{{{\W^{\rm im}}}}
\newcommand{\Wimd}{{{{\W^{\rm im}}^\dag}}}
\newcommand{\Wnt}{{{\W^{\rm {mfs}}_t}}}
\newcommand{\Wntd}{{{{\W^{\rm {mfs}}_t}^\dag}}}
\newcommand{\Wnp}{{{\W^{\rm mfs}_p}}}
\newcommand{\Wnpd}{{{{\W^{\rm mfs}_p}^\dag}}}
\newcommand{\Wnq}{{{\W^{\rm mfs}_q}}}
\newcommand{\Wnqd}{{{{\W^{\rm {mfs}}_q}^\dag}}}
\newcommand{\Wimn}{{{\W^{\rm im}_{\nu}}}}
\newcommand{\Wimnd}{{{{\W^{\rm im}_{\nu}}^\dag}}}

\newcommand{\wnt}{{w_{\nu}^t}}
\newcommand{\wnq}{{w_{\nu}^q}}
\newcommand{\wntq}{{w_{\nu}^{t+q}}}
%\newcommand{\Wntn}{{\tens{w^{\rm mfs}_{t,\nu}}}}
%\newcommand{\Wntnd}{{\tens{{w^{\rm mfs}_{t,\nu}}^\dag}}}
%\newcommand{\Wnpn}{{\tens{W^{\rm mfs}_{p,\nu}}}}
%\newcommand{\Wnpnd}{{\tens{{W^{\rm mfs}_{p,\nu}}^\dag}}}

@@

\newcommand{\Nt}{N_{\rm t}}
\newcommand{\Ns}{N_{\rm s}}
\newcommand{\Nc}{N_{\rm c}}

@@

\clearpage
\section{Scope of the document}

\clearpage
\section{Background}

@@

A canonical major/minor cycle algorithm is shown in Figure \ref{fig:majorminor}. The two functions Predict and MakeImage are sub-pipelines. ASKAPSoft and CASA both follow this form but with different ways of performing Predict (Figures \ref{fig:predictuv} and \ref{fig:predictimage}) and MakeImage (Figures \ref{fig:makeimageuv} and \ref{fig:makeimageimage})

@@

In the Multi-Scale CLEAN [RD??], the sky is modelled as a set of blobs. Performing this decomposition using a gradient search algorithm is very demanding of resources. Instead, in MSCLEAN, a greedy algorithm obtained by generalising the CLEAN algorithm is used. The greedy algorithm locates the amplitude, scale and location of the blob by a straightforward search in the set of residual images, each smoothed with the appropriate blob. For each minor cycle this produces an amplitude, location, and scale. The smoothed residual images and model images are updated, and iteration proceeds.

@@

The MSMFS algorithm decomposes the image into a set of $N_s$ blobs each with $N_t$ Taylor terms.

@@

Before performing any search, it is necessary to decouple the pixels in Taylor term space as well as possible. In practice, the Hessian (for each scale) for the peak of the PSF in Taylor term space is of modest size and can be inverted and used. The greedy algorithm then locates the scale and location in the reference-frequency image (as convolved with the set of scales). For each minor cycle this produces a location, scale, and values for all Taylor terms. The residual images and model images are updated, and iteration proceeds. The actual algorithm is shown in Figure \ref{fig:CASA}.

@@

\clearpage
\section{CASA and ASKAPsoft implementations}

The MS-MFS algorithm as implemented in CASA shown in Algorithm \ref{CASA}. The ASKAPsoft version is shown in Algorithm \ref{ASKAP} with the variant lines in red.

%\begin{figure}[htb]
%  \centering
%  \includegraphics[width=\textwidth]{./algorithm.pdf}
%  \caption{The MSMFS algorithm as implemented in CASA [RD??]}
%  \label{fig:algoCASA}
%\end{figure}

\begin{algorithm}
\scriptsize
  \SetLine
  \linesnumbered
  \dontprintsemicolon
%  \SetKwRepeat{Repeat}{Repeat}{Until}
%  \SetKwFor{ForEach}{ForEach}{Do}{End}
%\KwData{ $\vec{V}^{corr}_{\nu}, \vec{I}^{\rm shp}_s~\forall~s\in\{0,\Ns $-$1\}, ~ [\Sna]~ \forall \nu$ }
%\KwResult{ $\vec{I}^{\rm psf}_{{sp}\atop{tq}},[{H^{\rm peak}_s}], \vec{I}^m_{\nu_0}, \vec{I}^{\alpha}, \vec{I}^{\beta}$ }
  \KwData{calibrated visibilities : $\vec{V}^{\rm obs}_{\nu}~~\forall \nu$}
  \KwData{$uv$-sampling function and weights : $[{\Sa}_{\nu}], [\Wimn]$}
  \KwData{input : number of Taylor-terms $\Nt $, number of scales $\Ns $}
  \KwData{input : image noise threshold, $\sigma_{\rm thr}$, loop gain $g$}
  \KwData{input : scale basis functions : $\I^{\rm shp}_s ~ \forall s\in\{0,\Ns -1\}$}
  \KwData{input : reference frequency $\nu_0$ to compute $w_{\nu}=\dnuno$}
  \KwResult{model coefficient images : $\I^{\rm m}_{t}~ \forall t\in\{0,\Nt -1\}$}
  \KwResult{intensity, spectral index and curvature : $\I^{\rm m}_{\nuup_0},\I^{\rm m}_{\alphaup},\I^{\rm m}_{\betaup}$}

%{Compute the dirty image $\vec{I}^{\rm dirty}$ and psf $\vec{I}^{\rm psf}$}\;
  \For{ $t \in \{0,\Nt -1\}, q \in \{t,\Nt -1\}$}
  {
        { Compute the spectral Hessian kernel } $\vec{I}^{\rm psf}_{tq} = \sum_{\nu} \wntq \vec{I}^{\rm psf}_{\nu}$\;
        \For{ $s \in \{0,\Ns -1\}, p \in \{s,\Ns -1\}$}
	{
		{Compute scale-spectral kernels} $\vec{I}^{\rm psf}_{{sp}\atop{tq}} = \vec{I}^{\rm shp}_s \star \vec{I}^{\rm shp}_p \star \vec{I}^{\rm psf}_{tq} $\;
	}
  }
  \For { $s \in \{0,\Ns -1\}$}
  {
     Construct scale-dependent Taylor space Hessian $[{\He^{\rm peak}_s}]$ from $mid(\I^{\rm psf}_{{s,s}\atop{t,q}})$ and compute $[{\He^{\rm peak}_s}^{-1}]$\;
  }
%%%%%%%%%%%%%%%%%%%%%%
%%%\vspace{0.5cm}
%%  \caption[MS-MFS CLEAN : Pre-Deconvolution Setup]
%%          {MS-MFS CLEAN : Pre-Deconvolution Setup}
%%\end{algorithm}
%%%\newpage
%%
%%\begin{algorithm}[\He]
%%  \SetLine
%%  \linesnumbered
%%  \dontprintsemicolon
%%%%%%%%%%%%%%%%%%%%%%%  
%%\KwData{ $\vec{V}^{corr}_{\nu}, \vec{I}^{\rm shp}_s, \vec{I}^{\rm psf}_{{sp}\atop{tq}},[{H^{\rm peak}_s}]~~~\forall~~s \in \{0,\Ns -1\}, p \in \{s,\Ns -1\}, \sigma_{thr}$ }
%%\KwResult{$I^{\rm m}_{q}~ \forall q \in \{0,\Nt -1\}$}
%%%%%%%%%%%%%%%%%%%%%  
  Initialize the model $\vec{I}^{\rm m}_t$ for all $t \in \{0,\Nt -1\}$\; % and compute $f_{sidelobe}$ \;
%  \vspace{0.5cm} 
  \Repeat (\tcc*[f]{Major Cycle}) { Peak residual in $\vec{I}^{\rm res}_0 < \sigma_{\rm thr}$ }
  {
    \For{$t \in \{0,\Nt $-$1\}$}
    {
      Compute $\vec{I}^{\rm res}_t = \sum_{\nu} \wnt \vec{I}^{\rm res}_{\nu}$ from frequency-weighted residual images $\I^{\rm res}_{\nu}$\;
      \For{$s \in \{0,\Ns $-$1\}$}
      {
	    Convolve with $s^{th}$ scale-function $\vec{I}^{\rm res}_{{s}\atop{t}} = \vec{I}^{\rm shp}_s \star \vec{I}^{\rm res}_t$
      }
    }
    Calculate minor-cycle threshold $f_{\rm limit}$ from $\vec{I}^{\rm res}_{{0}\atop{0}}$\;
%  \vspace{0.5cm} 
    \Repeat (\tcc*[f]{Minor Cycle}){ Peak residual in $\vec{I}^{\rm res}_{{0}\atop{0}} < f_{\rm limit} $ } 
    {
%     Compute $I^{\rm m}_q~\forall q\in \{0.\Nt -1\}$ and update $\vec{I}^{\rm res}_{{s},{t}}~\forall s,t$ (Algorithm \vref{MSMFS_2})\;
     \For{$s \in \{0,\Ns $-$1\}$}
     {
%      \uIf{Peak of $\vec{I}^{\rm res}_{s,0} > 10~\sigma_{thr} $}
%      {
       \ForEach{pixel}
       {
          Construct $\I^{\rm rhs}_s$, an $\Nt \times 1$ vector from $\I^{\rm res}_{{s}\atop{t}} ~~\forall ~ t \in \{0,\Nt $-$1\}$\;
          Compute principal solution $\I^{\rm sol}_s = [{\He^{\rm peak}_s}^{-1}] \I^{\rm rhs}_s$\;
          Fill solution $\I^{\rm sol}_s$ into model images $\forall t$ : $\I^{\rm m,sol}_{{s}\atop{t}}$
       }
 %     }
  %    \Else
%      {
 %      Find the location of the peak in $\vec{I}^{\rm res}_{s,0},~\forall~s\in\{0,\Ns $-$1\}$\;
 %      Construct $I^{\rm rhs}_s$, from $I^{\rm res}_{s,t}$ for the chosen $s$, at this location\;
 %      Compute $I^{sol} = [{H^{\rm peak}_s}^{-1}] I^{\rm rhs}_s$ at this location\;
 %     }
    }
       Choose $\I^{\rm m}_{{p}\atop{t}} = max\{\I^{\rm m,sol}_{{s}\atop{t=0}},~\forall~s\in\{0,\Ns $-$1\}\}$ \;
       \For{$t \in \{0,\Nt -1\}$}
       {
        Update the model image : $\I^{\rm m}_t = I^{\rm m}_t + g ~[ \I^{\rm shp}_{p} \star \I^{\rm m}_{{p}\atop{t}}]$ \;
        \For{$s \in \{0,\Ns $-$1\}$}
	{
          Update the residual image : $\I^{\rm res}_{{s}\atop{t}} = \I^{\rm res}_{{s}\atop{t}} - g ~\sum_{q=0}^{\Nt -1}[\I^{\rm psf}_{{sp}\atop{tq}} \star \I^{\rm m}_{{p}\atop{t}}]$\;
	}
       }
    }
%  \vspace{0.5cm} 
   Compute model visibilities $\V^{\rm m}_{\nu}$ from  $\I^{\rm m}_t~\forall t\in \{0.\Nt -1\}$\;
   Compute residual visibilities $\V^{\rm res}_{\nu} = \V^{\rm obs}_{\nu}-\V^{\rm m}_{\nu}$\;
  }
  \vspace{0.5cm} 
Restore the model Taylor-coefficients $\I^{\rm m}_t~\forall t\in \{0.\Nt -1\}$ \;
Calculate $\vec{I}^{\rm m}_{\nuup_0}, \vec{I}^{\rm m}_{\alphaup}, \vec{I}^{\rm m}_{\betaup}$ from $\I^{\rm m}_t~\forall t\in \{0.\Nt -1\}$\;
If required, remove average primary beam : $\vec{I}^{\rm new}_{\nuup_0}=\vec{I}^{\rm m}_{\nuup_0}/\vec{P}_{\nuup_0};  \vec{I}^{\rm new}_{\alphaup}=\vec{I}^{\rm m}_{\alphaup}-\vec{P}_{\alphaup};  \vec{I}^{\rm new}_{\betaup}=\vec{I}^{\rm m}_{\betaup}-\vec{P}_{\betaup}$\;
%\vspace{0.5cm}

  \caption[MS-MFS Algorithm]
         {MS-MFS, as implemented in CASA}\label{CASA}

\end{algorithm}

\begin{algorithm}
\scriptsize
  \SetLine
  \linesnumbered
  \dontprintsemicolon
%  \SetKwRepeat{Repeat}{Repeat}{Until}
%  \SetKwFor{ForEach}{ForEach}{Do}{End}
%\KwData{ $\vec{V}^{corr}_{\nu}, \vec{I}^{\rm shp}_s~\forall~s\in\{0,\Ns $-$1\}, ~ [\Sna]~ \forall \nu$ }
%\KwResult{ $\vec{I}^{\rm psf}_{{sp}\atop{tq}},[{H^{\rm peak}_s}], \vec{I}^m_{\nu_0}, \vec{I}^{\alpha}, \vec{I}^{\beta}$ }
  \KwData{calibrated visibilities : $\vec{V}^{\rm obs}_{\nu}~~\forall \nu$}
  \KwData{$uv$-sampling function and weights : $[{\Sa}_{\nu}], [\Wimn]$}
  \KwData{input : number of Taylor-terms $\Nt $, number of scales $\Ns $}
  \KwData{input : image noise threshold, $\sigma_{\rm thr}$, loop gain $g$}
  \KwData{input : scale basis functions : $\I^{\rm shp}_s ~ \forall s\in\{0,\Ns -1\}$}
  \KwData{input : reference frequency $\nu_0$ to compute $w_{\nu}=\dnuno$}
  \KwResult{model coefficient images : $\I^{\rm m}_{t}~ \forall t\in\{0,\Nt -1\}$}
  \KwResult{intensity, spectral index and curvature : $\I^{\rm m}_{\nuup_0},\I^{\rm m}_{\alphaup},\I^{\rm m}_{\betaup}$}

%{Compute the dirty image $\vec{I}^{\rm dirty}$ and psf $\vec{I}^{\rm psf}$}\;
  \For{ $t \in \{0,\Nt -1\}, q \in \{t,\Nt -1\}$}
  {
{\color{red}        { Compute the spectral Hessian kernel $\vec{I}^{\rm psf}_{tq}$ from transform of frequency weight sampling } $\sum_{\nu} \wntq \Sa_{\nu}$\;}
        \For{ $s \in \{0,\Ns -1\}, p \in \{s,\Ns -1\}$}
	{
		{Compute scale-spectral kernels} $\vec{I}^{\rm psf}_{{sp}\atop{tq}} = \vec{I}^{\rm shp}_s \star \vec{I}^{\rm shp}_p \star \vec{I}^{\rm psf}_{tq} $\;
	}
  }
  \For { $s \in \{0,\Ns -1\}$}
  {
     Construct scale-dependent Taylor space Hessian $[{\He^{\rm peak}_s}]$ from $mid(\I^{\rm psf}_{{s,s}\atop{t,q}})$ and compute $[{\He^{\rm peak}_s}^{-1}]$\;
  }
%%%%%%%%%%%%%%%%%%%%%%
%%%\vspace{0.5cm}
%%  \caption[MS-MFS CLEAN : Pre-Deconvolution Setup]
%%          {MS-MFS CLEAN : Pre-Deconvolution Setup}
%%\end{algorithm}
%%%\newpage
%%
%%\begin{algorithm}[\He]
%%  \SetLine
%%  \linesnumbered
%%  \dontprintsemicolon
%%%%%%%%%%%%%%%%%%%%%%%  
%%\KwData{ $\vec{V}^{corr}_{\nu}, \vec{I}^{\rm shp}_s, \vec{I}^{\rm psf}_{{sp}\atop{tq}},[{H^{\rm peak}_s}]~~~\forall~~s \in \{0,\Ns -1\}, p \in \{s,\Ns -1\}, \sigma_{thr}$ }
%%\KwResult{$I^{\rm m}_{q}~ \forall q \in \{0,\Nt -1\}$}
%%%%%%%%%%%%%%%%%%%%%  
  Initialize the model $\vec{I}^{\rm m}_t$ for all $t \in \{0,\Nt -1\}$\; % and compute $f_{sidelobe}$ \; 
  \Repeat (\tcc*[f]{Major Cycle}) { Peak residual in $\vec{I}^{\rm res}_0 < \sigma_{\rm thr}$ }
  {
    \For{$t \in \{0,\Nt $-$1\}$}
    {
{\color{red}      Compute $\vec{I}^{\rm res}_t = \sum_{\nu} \wnt \vec{I}^{\rm res}_{\nu}$ from frequency-weighted residual visibilities $\V^{\rm res}_{\nu}$\;}
      \For{$s \in \{0,\Ns $-$1\}$}
      {
	    Convolve with $s^{th}$ scale-function $\vec{I}^{\rm res}_{{s}\atop{t}} = \vec{I}^{\rm shp}_s \star \vec{I}^{\rm res}_t$
      }
    }
    Calculate minor-cycle threshold $f_{\rm limit}$ from $\vec{I}^{\rm res}_{{0}\atop{0}}$\;
%  \vspace{0.5cm} 
    \Repeat (\tcc*[f]{Minor Cycle}){ Peak residual in $\vec{I}^{\rm res}_{{0}\atop{0}} < f_{\rm limit} $ } 
    {
%     Compute $I^{\rm m}_q~\forall q\in \{0.\Nt -1\}$ and update $\vec{I}^{\rm res}_{{s},{t}}~\forall s,t$ (Algorithm \vref{MSMFS_2})\;
     \For{$s \in \{0,\Ns $-$1\}$}
     {
%      \uIf{Peak of $\vec{I}^{\rm res}_{s,0} > 10~\sigma_{thr} $}
%      {
       \ForEach{pixel}
       {
          Construct $\I^{\rm rhs}_s$, an $\Nt \times 1$ vector from $\I^{\rm res}_{{s}\atop{t}} ~~\forall ~ t \in \{0,\Nt $-$1\}$\;
          Compute principal solution $\I^{\rm sol}_s = [{\He^{\rm peak}_s}^{-1}] \I^{\rm rhs}_s$\;
          Fill solution $\I^{\rm sol}_s$ into model images $\forall t$ : $\I^{\rm m,sol}_{{s}\atop{t}}$
       }
 %     }
  %    \Else
%      {
 %      Find the location of the peak in $\vec{I}^{\rm res}_{s,0},~\forall~s\in\{0,\Ns $-$1\}$\;
 %      Construct $I^{\rm rhs}_s$, from $I^{\rm res}_{s,t}$ for the chosen $s$, at this location\;
 %      Compute $I^{sol} = [{H^{\rm peak}_s}^{-1}] I^{\rm rhs}_s$ at this location\;
 %     }
     }
     Choose $\I^{\rm m}_{{p}\atop{t}} = max\{\I^{\rm m,sol}_{{s}\atop{t=0}},~\forall~s\in\{0,\Ns $-$1\}\}$ \;
       \For{$t \in \{0,\Nt -1\}$}
       {
        Update the model image : $\I^{\rm m}_t = I^{\rm m}_t + g ~[ \I^{\rm shp}_{p} \star \I^{\rm m}_{{p}\atop{t}}]$ \;
        \For{$s \in \{0,\Ns $-$1\}$}
	{
          Update the residual image : $\I^{\rm res}_{{s}\atop{t}} = \I^{\rm res}_{{s}\atop{t}} - g ~\sum_{q=0}^{\Nt -1}[\I^{\rm psf}_{{sp}\atop{tq}} \star \I^{\rm m}_{{p}\atop{t}}]$\;
	}
       }
    }
%  \vspace{0.5cm} 
   {\color{red} Compute model visibilities $\V^{\rm m}_{\nu}$ from  $\V^{\rm m}_t~\forall t\in \{0.\Nt -1\}$}\;
   Compute residual visibilities $\V^{\rm res}_{\nu} = \V^{\rm obs}_{\nu}-\V^{\rm m}_{\nu}$\;
  } 
Restore the model Taylor-coefficients $\I^{\rm m}_t~\forall t\in \{0.\Nt -1\}$ \;
Calculate $\vec{I}^{\rm m}_{\nuup_0}, \vec{I}^{\rm m}_{\alphaup}, \vec{I}^{\rm m}_{\betaup}$ from $\I^{\rm m}_t~\forall t\in \{0.\Nt -1\}$\;
If required, remove average primary beam : $\vec{I}^{\rm new}_{\nuup_0}=\vec{I}^{\rm m}_{\nuup_0}/\vec{P}_{\nuup_0};  \vec{I}^{\rm new}_{\alphaup}=\vec{I}^{\rm m}_{\alphaup}-\vec{P}_{\alphaup};  \vec{I}^{\rm new}_{\betaup}=\vec{I}^{\rm m}_{\betaup}-\vec{P}_{\betaup}$\;
%\vspace{0.5cm}

  \caption[MS-MFS Algorithm]
         {MS-MFS, as implemented in ASKAPsoft: {\color{red} red denotes difference from CASA}}\label{ASKAP}

\end{algorithm}

We can relate these back to the graphical form Figure \ref{fig:majorminor} by introducing variant sub pipelines for Predict and MakeImage. These are graphically shown in Figures \ref{fig:predictuv} to \ref{fig:makeimageimage}:

@@

The CASA and ASKAPsoft approaches should be equivalent apart from numerical differences such as due to the convolution function. Hence either can be used according to the most favourable scaling. Compared to CASA, ASKAPsoft does approximately two orders of magnitude less FFTs and 5 times as much gridding. Both forms should therefore be available in the SDP Performance Model and used as the context dictates.

The Minor Cycle is identical in CASA and ASKAPsoft. The Minor cycle is depicted graphically in Figure \ref{fig:minor}.

\begin{figure}[htb]
  \centering
  \includegraphics[width=\textwidth]{./MSMFS_Minor.pdf}
  \caption{Structure of Minor cycle for MSMFS as used in both CASA and ASKAPsoft.}
  \label{fig:minor}
\end{figure}

\clearpage
\section{Parallel processing}
\label{sec:parallel}

When moving the MSMFS algorithm to a distributed (loosely coupled) and parallel (tightly coupled) architecture such as the SDP architecture, there are a large number of important factors that must be considered.
\begin{description}
\item[Optimum partitioning] 
\item[Coupling across partitions] e.g. is the same pixel addressed in two different partitions? If so, is there a satisfactory approach to reconciling the two values?
\item[Synchronisation points] e.g. is a global synchronisation point required so that the deconvolutions can be made consistent? Is there an acceptable algorithm for reconciling separate facets?
\item[Amount of CU memory]
\item[Loading of CU memory backplane]
\item[Access to visibility store]
\end{description}

\subsection{Partitioning for Predict and MakeImage}
\label{subsec:partitoningpredictmakeimage}
